\vfill A Survey of Web Testing Frameworks and a Workflow for Testing Javascript Applications

### 2014-05-15 Paper/paper.tex
PX Description, another todo

@@

\subsubsection{PolyXpress Author}
Our tests covered the Authoring portion of PX.

>>>>

\subsubsection{Writing Unit Tests for Web Applications}
Writing unit tests for normal applications can be quite challenging. When there is the added overhead of network communication, it becomes exceptionally difficult to test units in isolation, i.e. without having to worry about bugs and time related to network code.

\todo{Expand}

@@

PolyXpress consists of three smaller application: 1) The Player. 2) The Author. 3) The PointKBFinder.

The Player is what the user open to actively complete stories. Using the Player, the user travels around and get notification when things are within range and can explore the story further. When the user opens the Player they can choose which story they want to play, including any they've made. The Player also gives them access to the PX Marketplace where all other public stories are available for download.

The Author is a tool to create one's own stories. Because our tests revolved around the Author, we'll be discussing it in depth in the following section, so to avoid redundency, we'll say nothing else here.

The PointFinder is a tool a user can use to select GPS points based on their current location. Setting points when authoring stories can be done by clicking on a map or using points saved in the PointFinder.

\subsubsection{PolyXpress Author}
Our tests covered the Authoring portion of PolyXpress. PolyXpress is a completely open application where users can publish and share their stories with the world of just among friends.

PolyXpress is meant for the general public and so there's no convuluted programming involved to create a story, it's all done through the application's Authoring tool. Screen captures of the authoring tool are in the appendix once again. The flow for creating a story is to create the Events first, the Chapters second, and finally tie it all together and create a Story. The flow is this way because the tool offers lists of existing Events in the Chapter creation page and lists of existing Chapters in the Story creation page. Doing the flow out of order or backwards would require a lot of editting of elements already created.

An Event consists of a title, a list of authors, a list of keywords, a version number, whether or not it's a recurring event, a geographical location (either entered manually as latitude and longitude, or using a map and clicking), a range at which this event can be triggered, and a number of assets to show the user when this event is triggered.

A Chapter consists of almost all the same things as an Event with the addition of an overview, an image, and a list of Events associated with that Chapter.

A Story consists of most of the same things as a Chapter except that the list of Events is a list of Chapters and the user chooses whether or not they want to publish this story. If the user chooses to share the story with the world, it is placed in the marketplace, otherwise it is stored within their own list of stories and is inaccesible to anyone else.
